Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-12-04 paper-kelompok/main.tex
dfd scaling
Add conclusion draft and revise FSM diagram

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.4]{system-dfd.png}}
    \caption{Level-1 Data Flow Diagram (DFD) of the system.}
    \label{system-dfd}
    \end{figure}

@@

\subsection{Repeatability}
\subsection{Wavelength Range}
\subsection{Resolution}
Resolution testing is carried out by calculating the resolution of the measurement results stored on an external SD card in the form of a CSV file.
The number of pixels needed for the absorbance spectrum measurement, which is obtained from the calibration results, is 297.
The absorbance measurement results are stored on an external SD card with a resolution that can be calculated using (\ref{resolution}).

@@

\section{Conclusions}

>>>>

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.27]{system-dfd.png}}
    \caption{Level-1 Data Flow Diagram (DFD) of the system.}
    \label{system-dfd}
    \end{figure}

@@

\subsection{Repeatability}
\subsection{Wavelength Range}
\subsection{Resolution}
Resolution testing is carried out by calculating the resolution of the measurement results stored on an external SD card in the form of a CSV file.
The number of pixels needed for the absorbance spectrum measurement, which is obtained from the calibration results, was 297.
The absorbance measurement results are stored on an external SD card with a resolution that can be calculated using Equation (\ref{resolution}).

@@

\section{Conclusions}
To support the study of spectrophotometry analysis in DMF platform, we describe the assembly of a portable spectrophotometer that can be integrated with a particular DMF system.
The portability makes on-the-go research processes easier.
Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
Measurement's accuracy of red, blue, and yellow food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Evolution 220 by Thermo Fisher Scientific).
The colorimetrice glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by ...
Future work will focus on...
